### 2017-07-05 KineticModel/estimation/docs/formulation/noisy_estimate.tex
changed formulation w/o ss constraints

	The bounds for the flux noise were set at (0,20) in the above problem.
\end{document}

>>>>

	The bounds for the flux noise were set at (0,20) in the above problem.

	\paragraph{Suggested modifications to address infeasibility (July 4)}
	After discussion with Prof. M, the following changes were made to the problem formulation:
	\begin{itemize}
		\item Experimental fluxes may/may not be at steady state. Accordingly, using the steady state constraint in the above formulation can render the optimization problem infeasible. Suggestion is to remove this constraint(s).
		\item Include the norm minimization constraint as an objective.
		\item Add the noise in fluxes and concentrations as part of the bound constraint.
		\begin{center}
			\begin{subequations}
				\begin{align}
				\underset{x,p_i}{\mathrm{min}} & \text{      }\left\Vert v_i-v^*\right\Vert\\
				& \text{      }v_i = f(x,p_i)\\
				& \text{      }x_{min}(1-\epsilon)\le x \le x_{max}(1+\epsilon)\\
				%& \text{      }v_{min}(1-\epsilon)\le v \le v_{max}(1+\epsilon)\\
				& \text{      }p_{i,min} \le p_i \le p_{i,max}\\
				\end{align}
			\end{subequations}
		\end{center}
	\item The noise $\epsilon$ is fixed at 5\% or 10\% to signify experimental noise.
	\end{itemize}

\end{document}
